Title

### 2018-08-26 thesis/paper/paper.tex
Added single best value

\begin{table}[H]
\caption{Single best value constraint (Q52060874)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement rank \\
\hline
Violation & \makecell{items with two constrained statements with rank preferred} \\
\hline
Dependency & all item statements and their rank \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item with the preferred rank. Thus the equation \ref{eq_no_separators_triple} is expanded to
\begin{equation}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation}

\subsubsection{With separators}
As in the case above, the qualifier non-existence and violation rules are very similar to single value. The only change is the addition of the rank requirements as shown below.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, W) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O) \wedge \\
&\text{qualifierEDB}(S, \{X\}, [X]) \wedge \\
&\text{qualifierEDB}(O, \{X\}, [X]) \wedge \\
&\text{does\_not\_have}(S, \{Y\}) \wedge \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}

>>>>

\begin{table}[H]
\caption{Single best value constraint (Q52060874)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement rank \\
\hline
Qualifiers & \makecell{separator (P4155) -- 0..* \\ qualifiers that must be different for exception} \\
\hline
Violation & \makecell{items with two constrained statements with rank preferred} \\
\hline
Dependency & all item statements and their rank \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

@@

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item with the preferred rank. Thus the equation \ref{eq_no_separators_triple} is expanded to
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation*}

\subsubsection{With separators}
As in the case above, the qualifier non-existence and violation rules are very similar to single value. The only change is the addition of the rank requirements as shown below.
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{rank}(S, \text{preferredRankConstant}) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, W) \wedge \\
&\text{rank}(O, \text{preferredRankConstant}) \wedge \\
&\text{unequal}(S, O) \wedge \\
&\text{has\_same}(S, O, \{X\}) \wedge \\
&\text{does\_not\_have}(S, \{Y\}) \wedge \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}
